\section{Organization}

This project follows the scrum framework. Meetings are performed in conformance with the scrum ceremonies. Management software is used to facilitate scrum and to track and plan progress. JIRA is the software of choice, containing the backlog, sprint backlog and burn-down charts. Additionally, a project plan is generated as a Gantt- diagram to ensure the project deadline is met. Project-cycles are fixed-length iterations, referred to as Sprints which have planned endings and start every other Tuesday, starting February $17^{th}$ $2017$.


\subsection{Work Hours}

The group has agreed that working hours are between 8:15 to 16:15, Thursday to Friday. This gives a total of 32 planned works hours per person in one week. One day a week is a nonworking day, preferably Saturday. Sundays will be utilized if additional work days are required. 


\subsection{Meetings}
In the second week of a sprint, Tuesday from 10:00 to 11:00 the sprint retrospective meeting is held. The team discuss and evaluate the last sprint, and learn from mistakes and successes. The wisdom gained in the retrospective meeting is noted and considered in the sprint planning meeting.\\
\\
After the retrospective meeting, Sprint planing meeting is held from 11:00 to 14:00. In this meeting, user-stories are   given a relative time-estimate called  story-points. Stories are divided into  tasks and shores that must be completed in order to achieve the sprint goal. The outcome is a product backlog with elaborated and estimated tasks. The team can take on any task or shore they see fit to work on.\\  
\\
Once a day, the group performs a daily stand-up meeting of no more than 15 minutes. This meeting is referred to as "daily Scrum" and starts 8:45 AM. \\
\\
Scrum reviews are performed after a sprint is ended. The planned days for these meetings are Fridays. The attendees are the team, product owner, scrum master, internal and, or external supervisors. Product increments produced in the last sprint is presented and discussed, any necessary changes and re-prioritization are made.
\\\\










